### 2021-07-05 rad-icfp-2021/purerad.tex

Finally, we add a new shift operator !shift1!. 
It takes an array of size $n$,  shifts all the element of the array by one, 
forgetting the last element, and puts a one in the first place. 
This somewhat ad-hoc operator naturally shows up when differentiating fold-like operators.

>>>>

Finally, we add two new shift operator !shift1L, shift1R!. 
They take an array of size $n$, and shift respectively forget the first and the last element of the array.
These somewhat ad-hoc operators naturally show up when differentiating fold-like operators.
